Cross Validation Analysis

### 2023-06-01 minos/validation/cross_validation.Rmd

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

>>>>

workingDir <- "/home/luke/Documents/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

compare_boxplot_long(pivoted.df = income.pivoted,
                     var = 'hh_income',
                     scen1 = 'raw',
                     scen2 = 'simulation')
